Accessing the nucleon tensor structure in inclusive deep inelastic scattering

### 2016-08-01 1607 - JMC for g2/Paper/JMC_dis.tex
Some conclusions added

\begin{abstract}
We revisit the standard analysis of inclusive DIS on protons taking into account the fact that on-shell quarks cannot be present in the final state, but they rather decay into hadrons. As a consequence, a spin-flip term associated with the invariant mass of this (mini)jet of hadrons is generated non perturbatively, and couples to the target's transversity distribution function. In inclusive cross sections, this provides an hitherto neglected and large contribution to the twist-3 part of the $g_2$ structure function, that can explain the discrepancy between recent calculations and fits of this quantity. It also provides an extension of the Burkardt-Cottingham sum rule, that puts stringent constraints on the small-$x$ behavior of the transversity function. Perspectives to measure the new spin flip term, and applications to spin-1 targets will be briefly discussed.
\end{abstract}

@@

A promising avenue to experimentally access jet functions is, however, through inclusive single hadron production, $e^+ e^- \to h X$, and inclusive dihadron 
production from the same hemisphere, $e^+ e^- \to h h X$, see 
Fig.~\ref{fig:epl_emn_h}.
In single-hadron production, the fragmentation functions $D_h$
play the role of PDFs in DIS, and couple to the jet functions
in an analogous way.
In double hadron production the enlarged number of Dirac structures
of the dihadron fragmentation correlator $D_{2h}$ allows one to access
the jet function in novel ways, and in particular to isolate the
contribution from the helicity-flip $J_0$ term.
Studying and classifying all the possibilities offered by single and
double hadron production will open up a rich phenom, which will in turn
be needed to extract pure twist-3 matrix elements from the $g_2$ structure function, and more in general to perform precise jet mass corrections in DIS.

{\bf [---------------- AA:  EDITED down here --------------------]}

It is important to explore in which other process does $\mj$ contribute, as to provide an experimental check of the formalism:
\begin{itemize}
\item inclusive $\Lambda$ production in $e^+ + e^-$
\item same-side dihadrons in $e^+ + e^-$ 
\end{itemize}
\todo{It would be cool to find a process where the $\mj$ contribution is the only one (similar to the BC breaking) ...}

@@

>>>>

\begin{abstract}
We revisit the standard analysis of inclusive Deep Inelastic Scattering (DIS)
off nucleons taking into
account the fact that on-shell quarks cannot be present in the final state,
but they rather decay into hadrons. As a consequence, a spin-flip term
associated with the invariant mass of the produced hadrons is generated
non perturbatively, and couples to the target's transversity distribution
function. In inclusive cross sections, this provides an hitherto neglected and
large contribution to the twist-3 part of the $g_2$ structure function, that
can explain the discrepancy between recent calculations and fits of this
quantity. It also provides an extension of the Burkardt-Cottingham sum rule,
that puts constraints on the small-$x$ behavior of the transversity
function and can help constraining the nucleon tensor charge.
%Perspectives to measure the new spin-flip term, and applications to
%spin-1 targets will be briefly discussed. 
\end{abstract}

@@

To experimentally measure jet functions and in particular the jet mass parameter, a promising avenue is throug inclusive single hadron production, $e^+ e^- \to h X$, and inclusive dihadron 
production from the same hemisphere, $e^+ e^- \to h h X$, see 
Fig.~\ref{fig:epl_emn_h}.
In single-hadron production, the fragmentation functions $D_h$
play the role of PDFs in DIS, and couple to the jet functions
in an analogous way. 
In double hadron production the enlarged number of Dirac structures
of the dihadron fragmentation correlator allows one to access
the jet function in novel ways, and in particular to isolate the
contribution from the helicity-flip $J_0$ term in combination with the
chiral-odd fragmentation function $H_1^{\sphericalangle}$.
Studying and classifying all the possibilities offered by single and
double hadron production will open up a rich phenomenology, which will in turn
be needed to extract pure twist-3 matrix elements from the $g_2$ structure function, and more in general to perform precise jet mass corrections in DIS.

@@

In this paper, we revisited the analysis of inclusive DIS, including the
effects due to the production of a system of final state hadrons, which we
conveniently referred to as ``jet.'' We described the jet in terms of a jet
correlator, corresponding to a 
nonperturbative cut propagator, different from the standard
perturbative propagator. We
carried out the
analysis of the jet correlator up to twist-3 level. The introduction of this jet correlator
leads to a difference in the expression of the structure function $g_2$ in
inclusive DIS with respect to the standard analysis: a new term appears, proportional to a jet mass
parameter and to the transversity distribution function. This new term
contributes to the violation of the Wandzura-Wilczek relation, in addition to
the standard pure twist-3 terms and quark mass corrections. Contrary to these
standard terms, however, the new jet mass correction violates also the
Burkhardt-Cottingham sum rule. This is yet another example of how surprising
and rich the phenomenology of polarized inclusive DIS can be. Detailed measurements of the $g_2$ structure
function can be used to constrain the jet mass parameter, the transversity
distribution function and the nucleon tensor charge, helping their extraction from other observables in, e.g.,
electron-positron annihilation and semi-inclusive DIS, respectively. The
knowledge of jet
mass parameter and transversity distribution will be eventually needed for a precise
extraction of pure twist-3 terms from the structure function $g_2$.
